---
title: "Assignment2"
author: "Pooja Patil"
date: "2022-10-15"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r }
rm(list=ls(all=TRUE)) #clears memory
options(digits=12) #keeps 12 digits in memory, otherwise summary statistics may be off due to rounding
```
#Set working directory by clicking on Session --> set working directory --> to source file loc
```{r }
sr_Data <- read.csv("stocks_return.csv", header=TRUE) # imports and renames dataset
sr_Data <- sr_Data[-1,] # remove one row
sr_Data #print data

```

```{r}
colnames(sr_Data) #print column name from the data
```
#Compute descriptive statistics
#Arithmatic Mean
```{r}
spmean <- round( mean(sr_Data[,"SR.SP.500"]), 1) # computes the mean and rounds it to the one decimal
applemean <- round( mean(sr_Data[,"SR.AAPL"]), 1)
intelmean <- round( mean(sr_Data[,"SR.INTC"]), 1)
krogermean <- round( mean(sr_Data[,"SR.KR"]), 1)
spmean
applemean
intelmean
krogermean

```
#Standard Deviation
```{r}
spsd <- round( sqrt(var(sr_Data[,"SR.SP.500"])), 1) # computes the SD and rounds it to the one decimal
applesd <- round( sqrt(var(sr_Data[,"SR.AAPL"])), 1)
intelsd <- round( sqrt(var(sr_Data[,"SR.INTC"])), 1)
krogersd <- round( sqrt(var(sr_Data[,"SR.KR"])), 1)
spsd
applesd
intelsd
spsd
```
#Geometric Mean
```{r}
#Geometric Mean for SP500
str(sr_Data$SR.SP500_Return) # confirm that variable called Return is numeric
sr_Data <- transform(sr_Data, returnplus1 = SR.SP500_Return + 1)
geomeanreturn <- exp(mean(log(sr_Data$returnplus1))) - 1

gm_sp500 <- round(geomeanreturn * 100, 1) 
gm_sp500
```

```{r}
#Geometric Mean for APPL
str(sr_Data$SR.AAPL_Return) # confirm that variable called Return is numeric
sr_Data <- transform(sr_Data, returnplus1 = SR.AAPL_Return + 1)
geomeanreturn <- exp(mean(log(sr_Data$returnplus1))) - 1
gm_apple <- round(geomeanreturn * 100, 1)
gm_apple
```

```{r}
#Geometric Mean of INTC
str(sr_Data$SR.INTC_Return) # confirm that variable called Return is numeric
sr_Data <- transform(sr_Data, returnplus1 = SR.INTC_Return + 1)
geomeanreturn <- exp(mean(log(sr_Data$returnplus1))) - 1
gm_intel <- round(geomeanreturn * 100, 1)
gm_intel

```

```{r}
#Geometric Mean of KR
str(sr_Data$SR.KR_Return) # confirm that variable called Return is numeric
sr_Data <- transform(sr_Data, returnplus1 = SR.KR_Return + 1)
geomeanreturn <- exp(mean(log(sr_Data$returnplus1))) - 1
geomeanreturn
gm_kroger <- round(geomeanreturn * 100, 1)
gm_kroger
```
##Extract variables to be used in the analyses
```{r}
sp500 <- sr_Data[,"SR.SP500_Return"] #no number before comma means select all rows
apple <- sr_Data[,"SR.AAPL_Return"]
```
#Regress SR.AAPL on SP.500
```{r}
mod.1 <- lm(apple ~ sp500)
summary(mod.1)
betaAAPL <- mod.1$coefficients[2]
round(betaAAPL,1)
```
# Plot data and regression line
```{r}
plot(sp500, apple)
abline(mod.1, col="red")
```
##Extract variables to be used in the analyses
```{r}
sp500 <- sr_Data[,"SR.SP500_Return"] #no number before comma means select all rows
intel <- sr_Data[,"SR.INTC"]
```

#Regress SR.INTC on SP 500
```{r}
mod.1 <- lm(intel ~ sp500)
summary(mod.1)
betaINTC <- mod.1$coefficients[2]
round(betaINTC, 1)

```
# Plot data and regression line
```{r}
plot(sp500, intel)
abline(mod.1, col="red")
```
##Extract variables to be used in the analyses
```{r}
sp500 <- sr_Data[,"SR.SP.500"] #no number before comma means select all rows
kroger <- sr_Data[,"SR.KR"]
```
#Regress SR.KR on SR.SP.500
```{r}
mod.1 <- lm(kroger ~ sp500) 
summary(mod.1)
betaKR <- mod.1$coefficients[2]
round(betaKR,1)

```
# Plot data and regression line
```{r}
plot(sp500, kroger)
abline(mod.1, col="red")
```
#Coefficients of variation
```{r}
#for SP500
round(coef_var_sp500 <- spsd / spmean, 1)
#for apple
round(coef_var_aapl <- applesd / applemean, 1)
#for intel
round(coef_var_intc <- intelsd / intelmean , 1)
#for kroger
round(coef_var_kroger <- krogersd / krogermean, 1)

```





